\documentclass[letterpaper,11pt]{article}

% Packages
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}

% Margins

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections Formatting

\titleformat{\section}{
    \vspace{-4pt}\scshape\raggedright\large
  }{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Custom Commands
    \newcommand{\resumeItemSmall}[2]{
        \item[]
        \small{
            \textbf{#1}{: #2 \vspace{-2pt}}
        }
    }

    \newcommand{\resumeItem}[2]{
    \item
    \small{
        \textbf{#1}{: #2 \vspace{-2pt}}
    }
    }

    \newcommand{\resumeSubheading}[4]{
    \vspace{-1pt}\item[]
        \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textbf{#1} & #2 \\
        \textit{\small#3} & \textit{\small #4} \\
        \end{tabular*}\vspace{-5pt}
    }

    \newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
    \newcommand{\resumeSubItemSmall}[2]{\resumeItemSmall{#1}{#2}\vspace{-4pt}}
    \renewcommand{\labelitemii}{$\circ$}
    \newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
    \newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
    \newcommand{\resumeItemListStart}{\begin{itemize}}
    \newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


%-------------------------------------------
%%%%%%%%%%%%% CV STARTS HERE %%%%%%%%%%%%%%% 

\begin{document}
    
    % Heading
        \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
            \textbf{\LARGE Nathan Beebe} \\
            \href{https://www.linkedin.com/in/nathan-beebe/}{https://www.linkedin.com/in/nathan-beebe/} & nbeebe@proton.me \\
            \href{https://github.com/hg-mercury-201}{https://github.com/hg-mercury-201} & 484-682-2444 \\
            
        \end{tabular*}

    % Experience
        \section{Experience}
         \resumeSubHeadingListStart

                \resumeSubheading{Boomi, LP.}{Remote}{Software Engineer}{Co-op, Oct. 2021 - Mar. 2022}
                \resumeItemListStart
                    \resumeItem{Java, Spring Framework, Maven}{Designed, tested, and developed backend web services to create reusable software artifacts to act as building blocks to unify all Boomi products utilizing Spring Framework concepts such as aspect oriented programming}
                    \resumeItem{Ubuntu 20.04 LTS}{Worked on developing features in a Linux environment heavily reliant on proprietary command line interface tools to use Docker containerized environments for development}
                    \resumeItem{JUnit, Mockito}{Utilized test driven development strategies to develop reliable code for features by testing against software requirements in integration tests and unit tests in Java testing frameworks}
                    \resumeItem{AWS}{Deployed features to test environments using Jenkins Build pipeline to ensure functionality is as expected when developing features}
                \resumeItemListEnd

                \resumeSubheading{iPipeline, Inc.}{Exton, PA}{.NET Developer}{Co-op, Sept. 2020 - Mar. 2021}
                \resumeItemListStart
                    \resumeItem{.NET Framework}{Worked as a Co-op developer in iPipeline's R\&D department. Used Visual Studio Pro and .NET Framework to develop a desktop application in C\# that automatically updates iGO Life insurance forms software for insurance agents.}
                    \resumeItem{GitHub Migration}{Worked on a team that was migrating and configuring .NET solutions to GitHub from Microsoft Azure DevOps TFS. Effort was to enable company to utilize an AWS Jenkins deployment solution.}
                \resumeItemListEnd

                \resumeSubheading{The Vanguard Group}{Malvern, PA}{Developer}{Co-op, Sept. 2019 - Mar. 2020}
                \resumeItemListStart
                    \resumeItem{Angular}{Developed component based front-end interfaces and unit tests for the Vanguard Financial Advice web application. System was used to input client information and generate long term financial plans.}
                    \resumeItem{Java}{Wrote back-end web service functions to handle data parameters sent to endpoints.}
                    \resumeItem{AWS}{Used DynamoDB to handle application cloud data storage.}
                    \resumeItem{Agile}{Developed features in 2-3 week sprints, featuring daily scrums, and backlog/assignment tracking in JIRA.}
                \resumeItemListEnd

                % \resumeSubheading{Sharing Excess, Inc.}{Philadelphia, PA}{Principal Developer}{Nov. 2018 - June 2019}
                % \resumeItemListStart
                %     \resumeItem{G Suite}{Setup short-term food data collection system using Forms and Sheets to record food donation data.}
                %     \resumeItem{MySQL}{Prototyped and designed database schema to handle food donation data and volunteer tracking/scheduling.}
                %     \resumeItem{HTML,CSS,PHP}{Prototyped front-end interfaces for organizational membership management.}
                % \resumeItemListEnd

            \resumeSubHeadingListEnd
    
    % Projects
        \section{Projects}

            \resumeSubHeadingListStart
                \resumeSubItemSmall{Entity Relation Diagram App}{Worked on buidling React web application to create detailed note taking tools for Dungeons and Dragons table top gaming.}
                \resumeSubItemSmall{Drexel EWB Website}{Volunteered for Drexel Engineers Without Borders chapter to develop a website for the organization. Used ReactJS hosted on Google Firebase hosting with custom domain name and Google Analytics package.}
                \resumeSubItemSmall{Local Ubuntu Server}{Repurposed old computer components to create a local network Ubuntu Server running version 20.04.}
                \resumeSubItemSmall{Dragon Pass Authenticator}{Worked on a team to develop an Android application which used NFC technology to protoype authentication into physical areas using a smartphone app. App used AWS EC2 to handle requests to a AWS RDS MySQL Server holding account details.}
            \resumeSubHeadingListEnd

    % Education
    \section{Education}
    \resumeSubHeadingListStart
        \resumeSubheading
        {Drexel University}{Philadelphia, PA}
        {B.S. Information Systems with Honors; GPA: 3.90, Summa Cum Laude}{September 2018 - June 2023}
    \resumeSubHeadingListEnd

    % Skills
        \section{Skills}
            \resumeSubHeadingListStart
            \item[]{
                \textbf{Languages}{: Python, Java, JavaScript (NodeJS), HTML, CSS, SQL}
                \hfill \\
                \textbf{Frameworks/Libraries}{: Angular, React.JS, Microsoft .NET, Spring} \\
                \textbf{Server Operating Systems}{: Windows Server, Ubuntu CLI 20.04} \\
                \textbf{Public Cloud}{: Amazon Web Services, Microsoft Azure DevOps Server (TFS)} \\
                \textbf{Collaboration Tools}{: Jenkins, Git/Bash, Atlassian JIRA, Confluence, and Bamboo Build Pipeline} \\
            }
            \resumeSubHeadingListEnd
    
        % \section{Interests}
        %     \resumeSubHeadingListStart
        %         \resumeSubItemSmall{PC Building}{I build high performance computers for games, programming, and music recording.}
        %         \resumeSubItemSmall{Music Recording}{I record music on my computer, and I am learning how to use Ableton Live digital audio software.}
        %         \resumeSubItemSmall{Guitar}{I have been playing electric, and acoustic guitar for 15 years, and I have played in multiple ensembles for charitable, personal, and education reasons.}
        %         \resumeSubItemSmall{Drexel Track Club}{I am a recreational runner with an interest in middle distance running, and personal fitness training.}
        %         \resumeSubItemSmall{Member of Drexel Engineers Without Borders}{Web Developer for the Drexel Engineers Without Borders chapter.}
        %     \resumeSubHeadingListEnd

\end{document}